---
title: "StormCloud: The Human and Economic Toll from U.S. Storms"
author: "Kevin Glass"
date: "`r Sys.Date()`"
output:
  html_document:
    toc:             true
    toc_depth:       3
    number_sections: true    
    toc_float:
      toc_collapsed: true
    theme:           united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Synopsis

# Code

## Introduction

The StormCloud code is complex and long; the uncommented base code is around 400 lines and the testing code (shown in the Appendix 1) is another 200 lines. Some of the techniques used to produce the code have not been discussed in class as are some of the libraries. As a result, the code will include extensive 

The


## Setup Phase
The Setup Phase is partitioned into four sections. The 


### StormCloud Libraries COMMENT


```{r setup phase, message=FALSE}

library(ggplot2)
library(dplyr)
library(cowplot)
library(knitr)
library(kableExtra)
```

### User Defined Constants
StormCloud gives the user control over the location and name of the required resource file. It also allows the user to select to select a state and county for more detailed analysis of the storm data.

```{r user defined constants}
URL      = 
  "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
DATAFILE = "storm.csv.bz2"

STATE_    <- "CA"
COUNTY_   <- "SAN BERNARDINO"

```

### Testing Constants
The following set of constants are used for debugging, testing, and notifying the user about the status of the programs execution. When running the code to produce useful output, all of these constants are set to FALSE.

```{r test constants}
VERBOSE                    = FALSE     # TRUE  FALSE
DEBUG                      = TRUE
UNIT                       = TRUE
SYSTEM                     = FALSE

ALL_FUNCTIONS              = FALSE
MAIN                       = FALSE
MAKE_STORM_COST_TABLES     = FALSE
DOWNLOAD_DATA_FILE         = FALSE
LOAD_STORM_COST_DATA       = FALSE
CLEAN_RAW_DATA             = FALSE
TRANSFORM_RAW_TO_BASE      = FALSE
MAKE_JURIS_STORM_LIST      = FALSE
GROUP_JURIS_COSTS          = FALSE

MAKE_RESULT_LIST           = TRUE
MAKE_STORM_COST_ANALYSIS   = TRUE

MAKE_STORM_COST_ANALYSIS   = FALSE
MAKE_TOP10_HUMAN_TABLE     = TRUE
MAKE_TOP10_ECONOMCIC_TABLE = FALSE
MAKE_CVC_IMAGE             = FALSE

PHASE_SETUP                = FALSE
PHASE_MAKE_DATA            = FALSE
PHASE_ANALYSIS             = FALSE
PHASE_CONTROL              = FALSE

DISPLAY_OUTPUT             = FALSE
```

### Program Constants
The program constants are used to make the code less cryptic. Rather than using numbers to define array indices, loop ranges, and other invariant values, StormCloud uses named constants. For example, the function MakeJurisStormList, uses a for loop with the range CNTY_BASE_IDX through US_BASE_IDX rather than 1 through 3. When the programmer knows the names of the constants, he or she does not need to remember which number represents which thing.

```{r program constants}

# All of the jurisdiction data (county, state, and U.S.) are stored in a 
# a jurisStormTable

EXECUTE           = 0
CNTY_BASE_IDX     = 1
ST_BASE_IDX       = 2
US_BASE_IDX       = 3

HUMAN_COST        = 1        
ECON_COST         = 2        

REGION_NAME = c('COUNTY', 'STATE', 'US',   
                'COUNTY_HUMAN_COST', 'STATE_HUMAN_COST', 
                'US_HUMAN_COST', 'COUNTY_ECON_COST', 
                'STATE_ECON_COST', 'US_ECON_COST')

# These constants are the column names for the final data frames
COUNTY_FIELD   <- 
  "c('EVTYPE', 'COUNTY', 'STATE', 'HUMAN_COST', 'ECON_COST')"

STATE_FIELD    <- 
  "c('EVTYPE', 'STATE', 'HUMAN_COST', 'ECON_COST')"
US_FIELD  <- 
  "c('EVTYPE', 'HUMAN_COST', 'ECON_COST')"

JURIS_FIELD     <- list(COUNTY_FIELD, STATE_FIELD, US_FIELD)

JURIS_FILTER    <-  list( 
  ".$'COUNTY' == COUNTY_ & .$'STATE' == STATE_",
  ".$'STATE' == STATE_",
  NULL
) # end JURIS_FILTER

```


<!-- 6789112345678921234567893123456789412345678951234567896123456789 -->
<!-- 
## 456789112345678921234567893123456789412345678951234567896123456789
 -->

## Program Control Phase

```{r program control phase}
Main <- function(url, datafile) {
  jurisCostList   <- MakeStormCostTables(url, datafile)
  resultList      <- MakeResultList(jurisTableList)
  
  if (VERBOSE) {
    print("That's all folks")
  }

  return (resultList)
}

```

## Make Data Frames Phase
<pre>
MakeStormCostTables
      |
      DownloadDataFile stores destfile in current directory
      |
      LoadStormCostData creates rawData from destfile and returns
      |                 a formatted variant
      |      
      ConsolidateStormTypes modifies and returns rawData
      |
      CleanRawData modifies and returns rawData
      |
      TransformRawToBase creates and returns baseData
      |
      MakeJurisStormList creates and returns jurisStormList
      |
      GroupJurisCost creates and returns jurisCostList
</pre>


### Make Storm Cost Tables

```{r make analysis phase}
MakeStormCostTables <- function(url, dataFile)  {
  if (VERBOSE & MAKE_STORM_COST_TABLES) {
    print("MakeStormCostTables(): coordinate the generation of ")
    print("the jurisTableList from the origional source file")
  }
  
  # If the data file is not in the project directory, download it ---  
  if (!file.exists(dataFile)) {
    DownloadDataFile(url, destfile)
  } else {
    if (VERBOSE & MAKE_STORM_COST_TABLES) {
      print(paste0(dataFile, " Contents already loaded "))
    }
  }
  if (DEBUG & MAKE_STORM_COST_TABLES) {
    print("Load")
  }

  rawData <- LoadStormCostData(dataFile)
  rawData <- ConsolidateStormTypes(rawData)
  rawData <- CleanRawData(rawData)
  ## Set up the aggregated financial and casualty data  -------------
  baseData <- TransformRawToBase(rawData)
  
  jurisStormList   <- MakeJurisStormList(baseData)
  jurisCostList    <- GroupJurisCost(jurisStormList)
  
  return (jurisCostList)
}  ## End of MakeStormCostTables function

```

### Download Data File

```{r}

# DownloadDataFile ##################################################
DownloadDataFile <- function(url, destfile)
{
  if (VERBOSE & DOWNLOAD_DATA_FILE) {
    print(paste0("downloadDataFile: Download ", destfile, " from\n", url))
  }

  retrieve = download.file(url, destfile, mode = "wb")
  if (is.null(retrieve)) {
    print("ERROR: could not access ", url)
    stop()
  }
}  ## End of DownloadDataFile function

```

### Load Storm Cost Data

```{r}

# LoadStormCostData ##################################################
# COUNTYNAME STATE  EVTYPE FATALITIES INJURIES PROPDMG PROPDMGEXP CROPDMG
LoadStormCostData <- function(dataFile)
{
  if ((VERBOSE | DEBUG) & LOAD_STORM_COST_DATA) {
    print(paste0("loadRawData: Reading raw storm data from ", 
                 dataFile))
  }

  ## set up table from the input file -------------------------------
  rawData <- read.table(dataFile, stringsAsFactors = FALSE, 
                        sep = ",",
                        colClasses = c(rep("NULL",5), NA, NA, NA, 
                                       rep("NULL",14), rep(NA, 6), 
                                       rep("NULL",9)),
                        header = TRUE)
  if(is.null(rawData)) {
    print(paste0("ERROR: could not read ", dataFile))
    stop()
  }
  
  if ((VERBOSE | DEBUG) & LOAD_STORM_COST_DATA) {
    print("LoadStormCostData: Display raw data ")
    print(head(rawData))
  }

  return (rawData)
}  ## End of LoadStormCostData function

```

### Clean Raw Data

```{r}

# CleanRawData ######################################################
CleanRawData <- function(rawData)
{
  if ((VERBOSE | DEBUG) & CLEAN_RAW_DATA) {
    print("CleanRawData: Set headers, transform data to numeric ")
    print(head(rawData))
  }

 ## convert data used for computation from string to numeric --------
  rawData <- rawData %>%
    mutate_at(c('FATALITIES', 'INJURIES', 'PROPDMG', 'CROPDMG'), 
              as.numeric)


  if ((VERBOSE | DEBUG) & CLEAN_RAW_DATA) {
    print("CleanRawData: check raw data")
    print(head(rawData))
  }
  return (rawData)
}  ## End of CleanRawData function

```

### Load Storm Cost Data

```{r}

# CleanRawData ######################################################
ConsolidateStormTypes <- function(rawData) {
  # this will be used to create a uniform name convention
  return (rawData)
}

```

### Transform Raw to Base

```{r}

# TransformRawToBase ##############################################
TransformRawToBase <- function(rawData) 
{
  if (VERBOSE & TRANSFORM_RAW_TO_BASE) {
    print("TransformRawToBase: aggregate economic and human costs")
    print(head(rawData))
  }

  baseData <- rawData %>% ungroup(.) %>%
    mutate (PROPDMGEXP = ifelse(PROPDMGEXP == 'K', 1000.,
                                ifelse(PROPDMGEXP == 'M', 
                                       1000000., 1.) ),
            CROPDMGEXP = ifelse(CROPDMGEXP == 'K', 1000.,
                                ifelse(CROPDMGEXP == 'M', 
                                       1000000., 1.) ),
            PROPDMG       = PROPDMG * PROPDMGEXP,
            CROPDMG       = CROPDMG * CROPDMGEXP,
            FATALITIES    = FATALITIES,
            INJURIES      = INJURIES,
            HUMAN_COST    = FATALITIES + INJURIES,
            ECON_COST     = PROPDMG + CROPDMG
            ) %>% 
    select(EVTYPE, COUNTYNAME, STATE, HUMAN_COST, ECON_COST)

  colnames(baseData) <- eval(parse(text = COUNTY_FIELD))

  if ((VERBOSE | DEBUG) & TRANSFORM_RAW_TO_BASE) {
    print("TransformRawToBase: check data after rename")
    print(head(baseData))
  }

  return (baseData)
}  ## End of TransformRawToBase function

```

### Make Jurisdiction Storm List

```{r}
# MakeJurisStormList ###########################################
MakeJurisStormList <- function(baseData) {
  if (VERBOSE & MAKE_JURIS_STORM_LIST) {
    print("MakeJurisStormList: make base data tables for each jursidiction")
  }

  jurisStormList = list()
  for (i in CNTY_BASE_IDX : US_BASE_IDX) {
    jurisStormData <- baseData %>%
      select(eval(parse(text = JURIS_FIELD[i])))

    if (!is.null(JURIS_FILTER[[i]])) {
      jurisStormData <- jurisStormData %>%
        filter(eval(parse(text = JURIS_FILTER[[i]])))
    }

    jurisStormList[[length(jurisStormList)+1]] <- jurisStormData
  }

  if (VERBOSE & MAKE_JURIS_STORM_LIST) {
    print("MakeJurisStormList: check source data frames")
    for (baseTable in jurisStormList) {
      print(head(jurisStormData))
    }
  }

  return(jurisStormList)
}  ## End of MakeJurisStormList function

```

### Group Juris Cost

```{r}

# GroupJurisCost ######################################################
GroupJurisCost <- function(jurisStormList)
{
  if (VERBOSE & GROUP_JURIS_COSTS) {
    print("GroupJurisCost: make an ordered list of human cost by ")
    print("jurisdiction")
  }
  
  jurisCostList = list()
  for (juris in jurisStormList)
  {
    if (DEBUG & GROUP_JURIS_COSTS) {
      print("GroupJurisCost: jurisCost type = pregrouping")
      print(paste0("GroupJurisCost: jurisCost type = ", class(juris)))
      print(head(juris, n = 10))
    }
    # jurisCost <- data.frame (juris)
    jurisStorm <- juris %>% group_by(EVTYPE)

    jurisCost <- jurisStorm %>%
    summarise_at(c("HUMAN_COST", "ECON_COST"), sum)

    jurisCost <- jurisCost %>% arrange(.$EVTYPE,
                                       .by_group = TRUE)

    if (DEBUG & GROUP_JURIS_COSTS) {
      print("GroupJurisCost: jurisCost type = postgrouping")
      print(head(jurisCost, n = 10))
    }
    jurisCostList[[length(jurisCostList)+1]] <- jurisCost

  }

  if (DEBUG & GROUP_JURIS_COSTS) {

    print("jurisStormTable: JurisCost")
    print(head(jurisCost))
  }
  
  return(jurisCostList)
} ## End of GroupJurisCost function

```

## Analysis Phase
<pre>
MakeResultsList
      |
</pre>

```{r analysis phase}

```

### Make Result List

```{r}

# GenerateResultsList ##########################################
MakeResultList <- function(jurisCostList) {
  if (VERBOSE & MAKE_STORM_COST_ANALYSIS) {
    print("MakeResultList: group the rawTables to jurisdiction ")
    print("tables grouped by storm type")
  }
  resultList <- list()
  ## Make StormCost Tables (Top 10)
  
  humanCost <- MakeTop10Tables(jurisCostList)

  # econCost  <- MakeTop10EconomicTable(jurisCostList)
  # 
  # ## Make Human v. Economic Cost Plots
  # cvcList <- MakeCvC(humanCost)
  # 
  # resultList[[length(resultList) + 1]] <- humanCost
  # resultList[[length(resultList) + 1]] <- econCost
  # resultList[[length(resultList) + 1]] <- cvcList
  # 
  return (resultList)
}

```

### Make Top 10 Tables

```{r}

# MakeTop10HumanTable ###########################################
MakeTop10Tables <- function(jurisTableList, type) {
  if ((VERBOSE | DEBUG) & MAKE_TOP10_HUMAN_TABLE) {
    print("MakeTop10HumanTable: starting data")
  }

  costList = list()
  for (juris in CNTY_BASE_IDX : US_BASE_IDX) {
    switch(type,
           cost <- jurisTableList[[juris]] %>% 
             arrange(desc(.$HUMAN_COST), .by_group = TRUE),
           cost <- jurisTableList[[juris]] %>% 
             arrange(desc(.$ECON_COST), .by_group = TRUE)
    )
    costList[[length(costList)+1]] <- cost
  }

  return(costList)
}

# MakeTop10EconomicTable ########################################
MakeTop10EconomicTable <- function(jurisTableList) {
  if ((VERBOSE | DEBUG) & MAKE_TOP10_ECONOMCIC_TABLE) {
    print("MakeTop10HumanTable: starting data")
    print(head(jurisTableList))
  }

  economicCostList = list()
  for (juris in CNTY_BASE_IDX : US_BASE_IDX) {
    economicCostTitle <- 
      switch (juris,
              paste0("Top 10 Storm Costs, (Human Costs)\n", 
                     COUNTY_, " ", STATE_),
              paste0("Top 10 Storm Costs, (Human Costs)\n",
                     state.name[grep(STATE_, state.abb)]),
              "Top 10 Storm Costs, (Human Costs\n)"
    )
    economicCostList[length(economicCostList) + 1] = economicCostTitle
    economicCostList[length(economicCostList) + 1] = 
      jurisTableList[juris + ECON_OFF]
  }

  return(economicCostList)
}
```


```{r}

makeOutputTables <- function(dataTables)
{
      humanCostTitle <- switch (juris, 
            paste0("Top 10 Storm Costs, (Human Costs)\n", 
                   COUNTY_, " ", STATE_),
            paste0("Top 10 Storm Costs, (Human Costs)\n",
                   state.name[grep(STATE_, state.abb)]),
            "Top 10 Storm Costs, (Human Costs\n)"
    )

  tableFmt <- kbl(head(dataTable[[2]], 10)) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), 
                  full_width = F, position = "left", 
                  font_size = 7)
  
 return (tableFmt)
}
```

### Make Images

```{r image phase}
MakeCvC <- function(cvcTable) {
  if ((VERBOSE | DEBUG) & MAKE_CVC_IMAGE) {
    print("MakeCvC: starting processing")
  }

  cvcImageList <- list()

  i <- 1
  for (cvcImage in cvcTable) {
    if (i %% 2 == 0) {
      df <- data.frame(cvcImage)
      # print(head(df))
      # collect plot attributes (i/2)
      sp <- ggplot(df, aes(x = STORM_HUMAN_COST, y = STORM_ECON_COST)) + geom_point()

      cvcImageList[[length(cvcImageList) + 1]] = sp
    } else {
      print(cvcImage)
    }
    i <- i + 1
  }

  return(cvcImageList)
}

```
## Execute
```{r execute phase}
if (EXECUTE) {
  results <- Main(URL, DATAFILE)
  
  humanList <- results[[1]]
  econList  <- results[[2]]
  cvcList   <- results[[3]]
}

```

<hr style="background: DarkOrchid; height: 3px"/>

<!-- https://www.dofactory.com/html/hr/style#:~:text=The%20style%20attribute%20specifies%20the,or%20an%20external%20CSS%20file -->

# Results

```{r}

```
# Bibliography

# Appendix 1: Testing Phase

```{r testing phase}

# ###################################################################
unit_LoadStormCostData <- function(url, datafile) {
  print("unit_LoadStormCostData")
  
  rawData <- LoadStormCostData(datafile)
  
  print("unit_LoadStormCostData raw data ###########################")

  print(head(rawData))
  
  print("###########################################################")

  return (rawData)
}

```

```{r}

unit_CleanRawData <- function(url, datafile) {
  rawData <- LoadStormCostData(datafile)
  cleanData <- CleanRawData(rawData)
  
  print("unit_CleanRawData cleaned data ###########################")
  print(head(cleanData))

  print("###########################################################")

  return (cleanData)
}

```

```{r}

unit_TransformRawToBase <- function(url, datafile) {
  rawData   <- LoadStormCostData(datafile)
  cleanData <- CleanRawData(rawData)
  baseData  <- TransformRawToBase(cleanData)
  
  print("unit_TransformRawToBase transformed data ###############")
  print(head(baseData))
  print("###########################################################")

  return (baseData)
}

```

```{r}

unit_MakeBaseTables <- function(url, datafile) {
  rawData <- LoadStormCostData(datafile)
  cleanData <- CleanRawData(rawData)
  baseData <- TransformRawToBase(cleanData)
  baseTableList <- MakeJurisStormList(baseData)
  
  print("unit_MakeBaseTables source disaster list ###########")
  for (baseTable in baseTableList) {
    print(head(baseTable))
  }

  return (baseTableList)
}

```
#### UNIT Get Human Cost
```{r}
unit_GroupJurisCost <- function(url, datafile) {
  rawData <- LoadStormCostData(datafile)
  cleanData <- CleanRawData(rawData)
  baseData <- TransformRawToBase(cleanData)
  baseTableList <- MakeJurisStormList(baseData)
  humanCost <- GroupJurisCost(baseTableList)
  
  print("unit_GroupJurisCost ###########")
  print("unit_GroupJurisCost: base data ---------")
  print(head(baseData, n = 3))
  
  print("unit_GroupJurisCost: base table ---------")
  for (baseTable in baseTableList) {
    print(head(baseTable, n = 3))
  }
  print("unit_GroupJurisCost: cost table ---------")
  for (cost in humanCost) {
    print(head(cost, n = 3))
  }

}
```

#### SYSTEM Make Storm Cost Tables

```{r}

system_MakeStormCostTables <- function(url, datafile) {
  jurisTableList <- MakeStormCostTables(url, datafile)

  i = 1
  for (jurisTable in jurisTableList) {
    print(paste0("List[", i, "]"))
    print(head(jurisTable))
    i = i + 1
  }
}

```

#### UNIT Make Top 10 Tables

```{r}
# ###################################################################
unit_MakeTop10Tables <- function(jurisTableList) {
  humanCostsTable <- MakeTop10Tables(jurisTableList, HUMAN_COST)

  i = 1
  for (humanCost in humanCostsTable) {
    print(paste0("unit_MakeTop10Tables: JurisList[", i, "]"))
    print(head(humanCost))
    i = i + 1
  }
  econCostsTable <- MakeTop10Tables(jurisTableList, ECON_COST)

  i = 1
  for (econCost in econCostsTable) {
    print(paste0("unit_MakeTop10Tables: JurisList[", i, "]"))
    print(head(econCost))
    i = i + 1
  }

}

```

```{r}

unit_MakeTop10EconomicTable <- function(jurisTableList) {
  economicCostsTable <- MakeTop10EconomicTable(jurisTableList)
  i = 1
  for (economicTable in economicCostsTable) {
    print(paste0("List[", i, "]"))
    if (i %% 2 == 0) {
      tbl <- data.frame(economicTable)
      print(head(tbl))
    } else {
      print(economicTable)
    }
    i = i + 1
  }
}

```

```{r}

if (SYSTEM & MAKE_STORM_COST_TABLES){
  print("MAKING Storm cost tables")
  system_MakeStormCostTables(URL, DATAFILE)
}
# 
# if (UNIT & LOAD_STORM_COST_DATA){
#   unit_LoadStormCostData(URL, DATAFILE)
# }
# 
# if (UNIT & CLEAN_RAW_DATA){
#   unit_CleanRawData(URL, DATAFILE)
# }
# 
# if (UNIT & TRANSFORM_RAW_TO_BASE){
#   unit_TransformRawToBase(URL, DATAFILE)
# }
# 
# if (UNIT & MAKE_JURIS_STORM_LIST){
#   unit_MakeBaseTables(URL, DATAFILE)
# }


if (UNIT & GROUP_JURIS_COSTS){
  unit_GroupJurisCost(URL, DATAFILE)
}
# 
#   
#   
# if (UNIT & MERGE_STORM_LIST){
#   unit_MergeStormLists(URL, DATAFILE)
# }
# 
# if (UNIT & GROUP_JURIS_COSTS){
#   unit_jurisStormTable(URL, DATAFILE)
# }


if (UNIT & MAKE_TOP10_HUMAN_TABLE){
  jurisCostList <- MakeStormCostTables(URL, DATAFILE)
  unit_MakeTop10Tables(jurisCostList)
}

```


<!-- MAKE_STORM_COST_ANALYSIS   = FALSE -->
<!-- MAKE_TOP10_HUMAN_TABLE     = FALSE -->
<!-- MAKE_TOP10_ECONOMCIC_TABLE = FALSE -->
<!-- MAKE_CVC_IMAGE             = FALSE -->


```{r}
# 
# 
# if (SYSTEM & PHASE_MAKE_DATA) {
#   rawData         <- unit_LoadStormCostData()
#   cleanData       <- unit_CleanRawData(rawData)
#   baseData        <- unit_TransformRawToBase(cleanData)
#   baseTableList   <- unit_MakeBaseTables(baseData)
#   jurisTableList  <- unit_jurisStormTable(baseTableList)
# }

```

# visualization tests

```{r visualization test}
# 
# unit_MakeCvC <- function(jurisTableList) {
#   humanList <- MakeTop10HumanTable(jurisTableList)
#   cvcImages <- MakeCvC(humanList)
# 
#   print(paste0("number of images = ", length(cvcImages)))
# 
#   i = 1
#   # plot(cvcImages[[1]])
# 
#   for (cvcImage in cvcImages) {
#     print(class(cvcImage))
# 
#     print(paste0("image[", i, "]"))
#     plot(cvcImage)
#     # dev.off()
#     i = i + 1
#   }
# }

```

```{r}
# 
# if (SYSTEM & PHASE_ANALYSIS) {
#   jurisTableList <- MakeStormCostTables(URL, DATAFILE)
#   resultList      <- GenerateResultsList(jurisTableList)
#   i = 1
#   for (jurisTable in resultList) {
#     print(paste0("List[", i, "]"))
#     print(head(jurisTable))
#     i = i + 1
#   }
# }
# 
# ```
# 
# ```{r}
# 
# if (UNIT & PHASE_ANALYSIS) {
#   jurisTableList <- MakeStormCostTables(URL, DATAFILE)
#   if (MAKE_TOP10_HUMAN_TABLE) {
#     humanList       <- unit_MakeTop10HumanTable(jurisTableList)
#   }
#   if (MAKE_TOP10_ECONOMCIC_TABLE) {
#     econList       <- unit_MakeTop10EconomicTable(jurisTableList)
#   }
#   if (MAKE_CVC_IMAGE) {
#     cvcImages      <- unit_MakeCvC(jurisTableList)
#   }
# }

```

```{r}

# if (DISPLAY_OUTPUT) {
#   jurisTableList <- MakeStormCostTables(URL, DATAFILE) 
#   tableSet <- makeOutputTables(jurisTableList[[US_BASE_IDX]])
#   tableSet
# }

```
